\documentclass[openany,11pt,papersize,dvipdfm,draft]{jsbook}
\usepackage[final]{funpro}
\usepackage{graphicx}

\def\hissu{\bgroup\color{red}}
\def\endhissu{\egroup}

\thisYear{2023}

\jProjectName{使ってもらって学ぶフィールド指向システムデザイン 2023}
\eProjectName{Field Oriented System Design Learning by Users' Feedback 2023}
\ProjectNumber{3-A}
\jGroupName{グループ~A}
\eGroupName{Group~A}

\ProjectLeader{佐々木虎太郎}{Kotaro~Sasaki}
\GroupLeader  {及川寛太}{Kanta~Oikawa}
\SumOfMembers{4}
\GroupMember {1}{及川寛太}{Kanta~Oikawa}
\GroupMember {2}{下村蒔里萌}{Marimo~Shimomura}
\GroupMember {3}{大津武琉}{Takeru~Otsu}
\GroupMember {4}{稲田敬介}{Keisuke~Inada}

\jadvisor{伊藤恵,南部美砂子,奥野拓,元木環,石尾隆}
\eadvisor{Kei~Ito,Misako~Nambu,Taku~Okuno,Tamaki~Motoki,Takashi~Ishio}

\jdate{2024年1月17日}
\edate{January~17, 2024}

\begin{document}
\maketitle

\frontmatter

\begin{jabstract}
　本プロジェクトは，フィールド調査をもとにした活動で発見した問題を，ITを用いて解決する．
これは，ユーザの仕事や生活をデザインし，地域や社会に貢献することが目的である．
本プロジェクトでは，アジャイル開発のスクラム手法を用いた．これは，迅速で柔軟な開発を行い，短期間の開発で効果的な成果を出すためである．
14名のメンバーが「交通」「小学校支援」「未来大生支援」のフィールドで活動した．
本報告では交通グループについての報告を行う．

　本グループでは，ブレインストーミングを行った中で発見したバスが使いにくいという問題を解決することを目的として活動してきた．
具体的には，いつバス停に行けばいいのかがわからない，乗りたいバスに間に合うかどうかがわからないという問題が存在する．
既存のバスロケーションアプリは情報量が多く，この問題を解決できていなかった．
また，バスの現在の正確な位置や，バス停への発着情報がわかりにくいという問題があった．
そこで，情報量が絞られており，一目でバスと自分の位置関係がわかるアプリの開発を検討した．
これまで，見やすいUI，洗練された機能についての考察，開発を行ってきた．
今後は，引き続き開発を進め，学内でのリリースを目指しながら取り組んでいく．

\begin{jkeyword}
バス，遅延，情報量過多，交通，モバイルアプリ，ひとめぼれ，デザイン，体験，アジャイル，スクラム，フィールド調査，函館
\end{jkeyword}
\bunseki{大津武琉}
\end{jabstract}

\begin{eabstract}
    This project aims to solve the problems found in field research using IT.
    This is to design the user's work and life, and contribute to the community and society.
    This project used the Scrum method of agile development method.
    The purpose is to quickly and flexibly develop and achieve effective results in a short period of development.
    15 members worked in the fields of "transportation", "elementary school support", and "FUN students support".
    This report is about eth transportation group.

    The group aims to solve the problem of inefficient use of buses found through brainstorming.
    Specifically, bus users have the problem of not knowing when to go to the bus stop and whether you will be able to catch the bus you want.
    Existing bus location apps have a lot of information and have not been able to solve this problem.
    In addition, the current location of the bus and the departure and arrival information to the bus stop are difficult to understand .
    Therefore, we considered developing an app that has a limited amount of information and can see the bus and your position relationship at a glance.
    So far, we have been developing a user interface that is easy to see and refined functions.
    We will continue to work on the development with the aim of releasing within the university.

\begin{ekeyword}
Bus, Delay, Information Overload, Transportation, Mobile App, Fall in Love at First Glance/Use, Design, Experience, Agile, Scrum, Field Research, Hakodate
\end{ekeyword}
\bunseki{大津武琉}
\end{eabstract}

\tableofcontents

\mainmatter

\include{background}
\include{product}
\include{activities}
\include{roadmap}
\include{learning}
\include{summary}

\begin{appendix}
\include{appendix_a}
\include{appendix_b}
\end{appendix}

\begin{thebibliography}{3}
    \bibitem {scrum} 西村 直人, 永瀬 美穂, 吉羽 龍太郎. SCRUM BOOT CAMP THE BOOK スクラムチームではじめるアジャイル開発. 株式会社 翔泳社. 2020.
    \bibitem {scrummaster} Zuzana Sochova. SCRUM MASTER THE BOOK. 株式会社 翔泳社. 2020.
    \bibitem {risk} 株式会社インターリスク総研,リスクマネジメント入門. \url{https://www.ms-ins.com/pdf/business/rm/rmguide.pdf} (2023/07/12)
\end{thebibliography}
\end{document}
